quollr: An R Package for Visualizing 2-D Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-08-18 paper-quollr.Rmd
Added Figure caption in HTML version for linked plots

```{r, echo=TRUE, eval=knitr::is_html_output(), fig.cap=""}
errornldrdt_link <- show_error_link_plots(
  point_data = df_exe, 
  edge_data = trimesh, 
  point_colour = clr_choice
)

@@

```{r model-limb, fig.cap="Compare the published $2-\\text{D}$ layout (Figure \\ref{fig:limb-rmse}b) and the $2-\\text{D}$ layout selected (Figure \\ref{fig:limb-rmse}f) by RMSE plot (Figure \\ref{fig:limb-rmse}) from the tSNE, UMAP, PHATE, TriMAP, and PaCMAP with different (hyper)parameters. The Limb muscle data ($n =  1067$) has seven close different shaped clusters in $10\\text{-}D$.", fig.pos='H', fig.width=15, fig.height=10, eval=knitr::is_latex_output()}

@@

```{r model-limb-html, eval=knitr::is_html_output(), fig.cap="Compare the published $2-\\text{D}$ layout (Figure \\@ref(fig:limb-rmse) b) and the $2-\\text{D}$ layout selected (Figure \\@ref(fig:limb-rmse) f) by RMSE plot (Figure \\@ref(fig:limb-rmse)) from the tSNE, UMAP, PHATE, TriMAP, and PaCMAP with different (hyper)parameters. The Limb muscle data ($n =  1067$) has seven close different shaped clusters in $10\\text{-}D$."}

>>>>

```{r, echo=TRUE, eval=knitr::is_html_output(), fig.cap="Link plot showing the relationship between the distribution of residuals (left), NLDR layout (middle) and the fitted model overlaid with the data in $7\\text{-}D$ (right)."}

errornldrdt_link <- show_error_link_plots(
  point_data = df_exe, 
  edge_data = trimesh, 
  point_colour = clr_choice
)

@@

```{r model-limb, fig.cap="Compare the published $2-\\text{D}$ layout (Figure \\ref{fig:limb-rmse}b) and the $2-\\text{D}$ layout selected (Figure \\ref{fig:limb-rmse}f) by RMSE plot (Figure \\ref{fig:limb-rmse}) from the tSNE, UMAP, PHATE, TriMAP, and PaCMAP with different hyper-parameters. The Limb muscle data ($n =  1067$) has seven close different shaped clusters in $10\\text{-}D$.", fig.pos='H', fig.width=15, fig.height=10, eval=knitr::is_latex_output()}

@@

```{r model-limb-html, eval=knitr::is_html_output(), fig.cap="Compare the published $2-\\text{D}$ layout (Figure \\@ref(fig:limb-rmse) b) and the $2-\\text{D}$ layout selected (Figure \\@ref(fig:limb-rmse) f) by RMSE plot (Figure \\@ref(fig:limb-rmse)) from the tSNE, UMAP, PHATE, TriMAP, and PaCMAP with different hyper-parameters. The Limb muscle data ($n =  1067$) has seven close different shaped clusters in $10\\text{-}D$."}

### 2025-08-18 paper-quollr.tex
Added Figure caption in HTML version for linked plots

\begin{figure}[H]
\includegraphics[width=1\linewidth]{paper-quollr_files/figure-latex/model-limb-1} \caption{Compare the published $2-\text{D}$ layout (Figure \ref{fig:limb-rmse}b) and the $2-\text{D}$ layout selected (Figure \ref{fig:limb-rmse}f) by RMSE plot (Figure \ref{fig:limb-rmse}) from the tSNE, UMAP, PHATE, TriMAP, and PaCMAP with different (hyper)parameters. The Limb muscle data ($n =  1067$) has seven close different shaped clusters in $10\text{-}D$.}\label{fig:model-limb}
\end{figure}

>>>>

\begin{figure}[H]
\includegraphics[width=1\linewidth]{paper-quollr_files/figure-latex/model-limb-1} \caption{Compare the published $2-\text{D}$ layout (Figure \ref{fig:limb-rmse}b) and the $2-\text{D}$ layout selected (Figure \ref{fig:limb-rmse}f) by RMSE plot (Figure \ref{fig:limb-rmse}) from the tSNE, UMAP, PHATE, TriMAP, and PaCMAP with different hyper-parameters. The Limb muscle data ($n =  1067$) has seven close different shaped clusters in $10\text{-}D$.}\label{fig:model-limb}
\end{figure}
